Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-05 R0V0.tex
Minor corrections

\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{berman_nonnegative_1994}. Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.

\mypara Further conditions are discussed in \cite{manchester_existence_2018}.

@@

\mypara The graph describing the network structure is provided in Figure~\ref{fig:graph}. Consider the case with $N=4$. To compute the matrix $W$, chordal graphs are employed.

@@

\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph} under different inputs. Figure~\ref{fig:Riemannian energy} show the Riemannian metric $V$ computed along solutions to network~\eqref{eq:example}. Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.

@@

\mypara When $N>8$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix inequality~\eqref{eq:MI:SSCCM} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

The parser took 98  seconds to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has elements defined, for every $q\in\mathbb{R}^8$, by
\begin{align*}
	\overline{Y}_i(q)=&-2\begin{bmatrix}
	y_i&1+\sum_{k=1}^4 y_k^2+x_k^2
	\end{bmatrix},\\
	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},\\
	0_{1\times2}=&\begin{bmatrix}0,&0\end{bmatrix},
\end{align*}
where $i\in\mathbb{N}_{[1,4]}$, and structure given by the matrix
\begin{equation}\label{eq:example:Y:general}
		\resizebox*{0.85\columnwidth}{!}{$\begin{bmatrix}
			\overline{Y}_1(q),&0_{1\times 2},&-0.03\hat{Y}_1(q),&0_{1\times2}\\
			0_{1\times 2},&\overline{Y}_2(q),&0_{1\times 2},&-0.04\hat{Y}_2(q)\\
			-0.04\hat{Y}_3(q),&0_{1\times 2},&\overline{Y}_3(q),&0_{1\times 2}\\
			0_{1\times 2},&-0.03\hat{Y}_4(q),&0_{1\times 2},&\overline{Y}_4(q)
		\end{bmatrix}$}.
\end{equation}

\mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$. The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 2.6 seconds, the matrix $W$ is given by
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&98s\\
	Neighbor&3.5s\\
	Fully decentralized&2.6s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
	\label{tab:chain case}
\end{table}

>>>>

\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{berman_nonnegative_1994}. Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive. Further conditions are discussed in \cite{manchester_existence_2018}.

@@

\mypara The graph describing the network structure is provided in Figure~\ref{fig:graph}. Consider the case with $N=4$ to compute the matrix $W$, chordal graphs are employed.

@@

\mypara When $N>8$ and $Y$ is a full-rank matrix with elements described by polynomials, the set of matrix inequalities~\eqref{eq:main result} could not be solved on a standard desktop computer. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix inequality~\eqref{eq:MI:SSCCM} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position of the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

\mypara The solver took 98  seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has elements defined, for every $q\in\mathbb{R}^8$, by
\begin{align*}
	\overline{Y}_i(q)=&-2\begin{bmatrix}
	y_i&1+\sum_{k=1}^4 y_k^2+x_k^2
	\end{bmatrix},\\
	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},\\
	0_{1\times2}=&\begin{bmatrix}0,&0\end{bmatrix},
\end{align*}
where $i\in\mathbb{N}_{[1,4]}$, and structure given by the matrix
\begin{equation}\label{eq:example:Y:general}
		\resizebox*{0.85\columnwidth}{!}{$\begin{bmatrix}
			\overline{Y}_1(q),&0_{1\times 2},&-0.03\hat{Y}_1(q),&0_{1\times2}\\
			0_{1\times 2},&\overline{Y}_2(q),&0_{1\times 2},&-0.04\hat{Y}_2(q)\\
			-0.04\hat{Y}_3(q),&0_{1\times 2},&\overline{Y}_3(q),&0_{1\times 2}\\
			0_{1\times 2},&-0.03\hat{Y}_4(q),&0_{1\times 2},&\overline{Y}_4(q)
		\end{bmatrix}$}.
\end{equation}

\mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$. The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 4.4 seconds, the matrix $W$ is given by
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}

\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph}, according to each constraint imposed on the controller. Figure~\ref{fig:Riemannian energy} show the Riemannian metric $V$ computed along solutions to network~\eqref{eq:example}. Note that, when random initial random initial conditions are considered and the input is zero to be identically zero, the system may diverge from the neighborhood of the origin.

@@

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&98s\\
	Neighbor&3.5s\\
	Fully decentralized&4.4s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
	\label{tab:chain case}
\end{table}
